\vspace{1.0cm} \Large \bf Integrating influenza antigenic dynamics with molecular evolution

### 2013-07-24 flux.tex
Minor revision.

%%% map %%%
\begin{figure}[h]
	\centering		
	\includegraphics[width=1.0\textwidth]{figures/seq_grid}
	\caption{\textbf{Pairwise correlations between genetic distance, measured as amino acid mutations or as phylogenetic distance, and antigenic distance for influenza A/H3N2, A/H1N1, B/Vic and B/Yam.} 
	The top row shows correlations between number of amino acid mutations and average antigenic distance between 10,000 random pairs of viruses.
	The bottom row shows correlations between average phylogenetic distance, measured in terms of years, and average antigenic distance between 10,000 random pairs of viruses.
	Dashed lines show linear model fits, with $R^2$ and slope noted, while solid lines show LOESS fits.
	Antigenic distances derive from model 2 of Table \ref{errortable}.
	} 
	\label{seq_grid} 
\end{figure}

>>>>

%%% map %%%
\begin{figure}[h]
	\centering		
	\includegraphics[width=1.0\textwidth]{figures/seq_grid}
	\caption{\textbf{Pairwise correlations between genetic distance, measured as amino acid mutations or as phylogenetic distance, and antigenic distance for influenza A/H3N2, A/H1N1, B/Vic and B/Yam.} 
	The top row shows correlations between number of amino acid mutations in HA1 and average antigenic distance between 10,000 random pairs of viruses.
	The bottom row shows correlations between average phylogenetic distance, measured in terms of years, and average antigenic distance between 10,000 random pairs of viruses.
	Dashed lines show linear model fits, with $R^2$ and slope noted, while solid lines show LOESS fits.
	Antigenic distances derive from model 2 of Table \ref{errortable}.
	} 
	\label{seq_grid} 
\end{figure}
